%
%      CAREER HIGHLIGHTS
%
\section{Career Highlights}
%
% Development
%
\ifthenelse{\equal{\jobname}{\development}}{%
        \subsection{\href{https://github.com/runcrypto/static-discharge}
        {Prototype contactless bitcoin lightning payments}}
        \ifthenelse{\boolean{pdf}}{%
            Add functionality to open source mobile wallet and build terminal
            with R-PI and RC532 breakout board
            \vspace{5pt}
        }{%
          % Situation
            For my entry in the second boltathon (lightning hackathon) I wanted
            to address a UX issue with using mobile wallets.\\
          % Target
            The existing payment methods in the market from Google and Apple
            all utilise Near Field Communication (NFC) to provide contactless
            payment.  This was not available for bitcoin lightning wallets.\\
          % Action
            The solution involved creating a payment requester terminal from a
            a Raspberry PI with a RC532 breakout board and a mobile device
            running a bitcoin lightning wallet which I would add NFC
            functionality to.\\
          % Result
            I was able to produce a prototype terminal and extend the open
            source zap-android wallet, the enhancement was refined and merged
            into the main project.\\
            \href{https://github.com/LN-Zap/zap-android/issues/158}{see on github}
        }

    \subsection{Migration of documentation to multi platform publishing}
        \ifthenelse{\boolean{pdf}}{%
	        Improved quality, reduced duplication and decoupled content from
            presentation
            \vspace{5pt}
        }{%
          % Situation
            The acquisition of the company required rebranding our customer
            facing documentation.  Reworking the word documents was going to be
            a costly exercise taking 2 weeks.\\
          % Target
            I wanted to introduce a document life-cycle process and improve
            the management of content so that it could adapt to future
            requirements with minimal overhead.\\
          % Action
            To tackle the management of content I migrated the content to a
            markup language.  This allowed the content to be decoupled from the
            presentation.  Git and JIRA were used to implement continuous
            improvement.\\
          % Result
            The consistency and accuracy of documentation has benefited.  With
            changes to branding being able to be applied across the content in
            4 hours rather than 2 weeks.  In addition to PDF documentation we
            have also been able to publish the same content to HTML.
        }

	\subsection{Develop components and design patterns for DSL}
        \ifthenelse{\boolean{pdf}}{%
	        Reduction in code reuse and defects for scripting projects
            \vspace{5pt}
        }{%
          % Situation
            Many solutions required the same or similar features that would be 
            scripted for each project. This resulted in duplicate of effort and 
            a high number of defects.\\
          % Target
            By creating a component library we could reduce the production time 
            and increase the quality of solutions provided.\\
          % Action
            I produced a business case for the creation of a set of standard
            components that was well received and gained approval for a proof 
            of concept.  This became the first component of many that was 
            produced and was able to be managed through a formal SDLC.\\
          % Result
            The average amount for time required to produce scripts was reduced 
            by 40\%.  Defects were reduced and resolutions made easier as they 
            were typically configuration related rather than bugs in the script.
        }
}{}
%
% Management
%
\ifthenelse{\equal{\jobname}{\management}}{%
  \subsection{Project Productization}
    \ifthenelse{\boolean{pdf}}{%
          Successfully transitioned several projects to products through
          redesign and introduction of new processes.  Mentoring teams
          through the transformation and providing technical leadership,
          setting expectations to other areas of the business.\\
    }{%
          % Situation
          A software project for a large customer site had been successfully
          completed and other sites were keen to implement it at their own
          sites.\\
          % Target
          There was another site in project and dozens of others that were
          also being targeted as consumers of the application.  We needed to
          ensure that the application could be managed as a single product
          and not a collection of individual projects.\\
          % Action
          To secure the investment by Netcall I produced a business case for
          migrating to a product development model.  Whilst awaiting approval,
          I led the development ensuring that the additional features would
          allow for a stategic migration.\\
          % Result
          The second project was completed and at the start of the third
          project we were able to fully transition to a product methodology
          and build out the infrastructure and processes for governance of
          the new product.
    }

    \subsection{Upgrade Role-out}
	    \ifthenelse{\boolean{pdf}}{%
            Successfully managed processes and capacity through aggressive
            roll-out of software update to 300 customers over 18 months at
            Advanced.  The project was completed before the hard deadline when
            Adobe Flash was disabled in Jan 2021.\\
	    }{%
            % Situation
            Adobe announced in 2018 that Flash would no longer work after Jan
            2021.  Several software components used Flash that would need to
            upgraded.\\
            % Target
            We had around 300 customers to upgrade in an 18 month period with
            no scope for moving the deadline.  Each upgrade project was to
            average a 6 week life-cycle and included one or more test systems.\\
            % Action
            Working a member of the  programme committee I managed the
            resource capacity planning and provided feedback on opportunities
            to improve processes.\\
            % Result
            The programme was completed with only 8 customers not upgraded by
            the time that Flash was retired.  The weekly update meetings with
            the team were effective at building trust, collaboration, sharing
            information and strengthening performance.
	    }

	\subsection{Establishing Technical Account Manager role}
        \ifthenelse{\boolean{pdf}}{%
            Lead the development of processes and relationships in the new role
            of technical account manager and customer success team at eGain.
            Engaging with key customers to drive new revenue and retention.
            \vspace{5pt}
        }{%
          % Situation
            As a part of the customer success strategy, the business wanted to 
            provide technical leadership and governance to key customers.\\
          % Target
            A new Technical Account Manager role needed to be established and 
            rolled out to key customers.  This would provide technical 
            leadership of issue resolution and project delivery.\\
          % Action
            In a team of 6 technical consultants, across 3 continents we defined
            the scope of the role, documented the initial processes and a
            continuous improvement framework.\\
          % Result
            Over the first 6 months we were able to onboard 7 key accounts in
            EMEA, reduce the issue backlog of these accounts from 64 to 38 and 
            successfully mediate several project delivery conflicts.
        }

    % \subsection{Leading change to Agile Methodologies}
    %     \ifthenelse{\boolean{pdf}}{%
    %         Delivered change through research and training the Professional
    %         Services delivery team, transitioning to an Agile Development
    %         workflows.  A part of a company wide initiative at Pitney Bowes
    %         Software working with Mike Cohn of Mountain Goat Software.
    %         \vspace{5pt}
    %     }{%
    %         % Situation
    %         Pitney Bowes Software consisted of several mature products that
    %         were managed with a traditional waterfall methodology.
    %         % Target
    %         As a part of a strategic change program, the development life-cycle
    %         and professional services delivery frameworks were to adopt an
    %         agile approach.
    %         % Action
    %         As the professional services representative in the program, I
    %         researched and attended training sessions with Mike Cohn of
    %         Mountain Goat Software to provide an implementation plan to the
    %         management team and deliver training to the other team members.
    %         % Result
    %         Over 3 months we were able to start delivering agile project
    %         management and iterative delivery of solutions which decreased the
    %         defects through the increased test cycles.
    %     }
}{}
