%
%
%     EDUCATION
%
\section{Professional Training}
%
% Common
%
\subsection{\href{https://www.udemy.com/certificate/UC-a8db49e4-26b6-4fa6-b156-d1cc5423de7f/}{Microservices Architecture - The Complete Guide}}
Memi Lavi \textit{2023}
    \ifthenelse{\boolean{pdf}}{\vspace{5pt}}{
    Udemy course with lectures providing a deep dive into Microservices aimed at Software Architects.
}
\subsection{\href{https://www.udemy.com/certificate/UC-fbe5142e-d448-439a-a4b9-59893a0102ba/}{The Complete Guide to Becoming a Software Architect}}
Memi Lavi \textit{2023}
    \ifthenelse{\boolean{pdf}}{\vspace{5pt}}{
    Udemy course with lectures providing an overview of Software Architecture processes and design patterns.
}
%
% Development
%	
\ifthenelse{\equal{\jobname}{\development}}{

    \subsection{\href{https://www.udemy.com/certificate/UC-df045ecc-7d0c-419c-ab03-3d5ab4a6c8d2/}{Design Patterns in Modern C++}}
    Udemy \textit{2021}
    \ifthenelse{\boolean{pdf}}{\vspace{5pt}}{
        This course provides a comprehensive overview of Design Patterns in Modern C++ from a practical perspective.}
    \vspace{5pt}	
	\subsection{\href{https://www.udemy.com/certificate/UC-52d0b523-203a-41e5-9597-e71dd5121a0b/}{Beginning C++ Programming}}
    Udemy \textit{2020}
    \ifthenelse{\boolean{pdf}}{\vspace{5pt}}{
        Modern C++ Object-Oriented Programming (OOP) and STL skills needed for
        game, system, and application development.}
	\subsection{\href{https://www.udemy.com/certificate/UC-84c0cc58-82c7-4f03-9bec-ae5e9f681fed/}{Complete Node.js Developer}}
	Udemy \textit{2020}
    \ifthenelse{\boolean{pdf}}{\vspace{5pt}}{
        Learn Node.js by building real-world applications with Node, Express, 
        MongoDB, Jest.  This included:
        \begin{itemize}
            \item Writing API's for a task-manager app
            \item Using weather and geolocation API's to create a weather app
            \item Using web sockets to create a real-time chat app
        \end{itemize}
    }
	\subsection{\href{https://www.eventbrite.com/e/applied-blockchain-lab-developing-smart-contracts-tickets-40715007684}{Smart Contracts}}
	Applied Blockchain Labs \textit{2018}
    \ifthenelse{\boolean{pdf}}{\vspace{5pt}}{
        This one day workshop included an introduction to Blockchain Technology,
        it's use cases and ideas for projects.  It went on to give practical
        tutorials on Ethereum smart contracts to create ERC20 tokens and
        creating an online wallet for Ethereum.}
	\subsection{Writing Queries Using SQL}

	QA Learning \textit{2012}
    \ifthenelse{\boolean{pdf}}{\vspace{5pt}}{
        This 2 day course taught basic knowledge and skills to create queries 
        using T-SQL. How to select, filter and sort data from multiple tables 
        and how to use views and stored procedures.}
    \\
}{}
%
% Management
%
\ifthenelse{\equal{\jobname}{\management}}{
	
	\subsection{\href{https://www.qa.com/course-catalogue/courses/itil-3-foundation-certificate-in-it-service-management-with-exam-itilf/}{ITIL v3 Foundation}}
	QA Learning \textit{2017}
    \ifthenelse{\boolean{pdf}}{\vspace{5pt}}{
        ITIL Foundation teaches the fundamentals of the
        IT Infrastructure Library (ITIL) core volumes, which provide an
        end-to-end view of IT and its integration with business strategy. Those
        core volumes are: Service Strategy, Service Design, Service Transition,
        Service Operation and Continual Service Improvement.}
	
}{}
%
% Common
%
\subsection{\href{https://www.slideshare.net/aslamkhn/lean-in-software-development}{Leaders in Agile series}}
Kent Beck, Aslam Khan, Henrik Kniberg \textit{2011}
    \ifthenelse{\boolean{pdf}}{\vspace{5pt}}{
    A series of 5 webinars, sponsered by SD Times, covering a variety of
    aspects of Agile software developemnt methodologies and tools including:
    Test Driven Development, Lean, Kanban, Scrum.
}
	
\subsection{\href{https://www.mountaingoatsoftware.com/training/courses/agile-estimating-planning}{Agile Estimating and Planning}}
Mountain Goat Software \textit{2011}
    \ifthenelse{\boolean{pdf}}{\vspace{5pt}}{
    This 3 day course was conducted in-house at Pitney Bowes with visiting 
    trainer Mike Cohn.  The course covered an overview of Agile
    Methodologies, writing user stories, estimating, sprints and scrum.
}
