%
% Personal Statement
%
\ifthenelse{\equal{\jobname}{\development}}{
Experienced Software Developer adept in bringing forth expertise in design,
installation, testing and maintenance of software systems. Equipped with a
diverse and promising skill-set. Proficient in various platforms, languages,
and embedded systems. Experienced with the latest cutting edge development
tools and procedures.  Able to effectively self-manage during independent
projects, as well as collaborate as part of a productive team.}{}
\ifthenelse{\equal{\jobname}{\management}}{
A forward thinking strategist and customer-centric Technical Leader with over
20 years experience within high-pressure environments, providing technical
expertise for business critical software; a strong leader and relationship
builder with clients, partners and technology vendors, trusted professional
with accountability for KPIs and SLAs targets. Brings to the fore, governance,
service management, and continuous improvement, as well as key client and
stakeholder engagement. Calm and analytical with exceptional team collaboration
and mentoring skills; proven ability to create sustainable, scalable and high
performing solutions closely aligned with clients expectations and service
requirements. Consistently demonstrates high standards of professionalism and
integrity, and applies sound judgement to decision-making processes. Renowned
as a strong and supportive Team Leader committed to the achievement of
individual and company shared goals.}{}
